### 2021-06-03 background.tex
first update - little grammar corrections

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software. Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, 
working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.

Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps. Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}. For security reasons, Google play list each app with the requested permission. However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}. Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product.~\cite{DBLP:conf/soups/FeltHEHCW12} 
%\kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}

Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code~\cite{DBLP:journals/corr/abs-2002-04540}
%\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
, calling java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls. Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access. Those are kind of attack that usually tackled with the Android Mining Sandbox \cite{DBLP:conf/icse/JamrozikSZ16}.

@@

\textbf{The Android Mining Sandbox} concept is a sandboxing technique that consists of mining rules from an android app, and use these rules to ensure system security. The sandboxing technique comprises of two steps. First, rules are mined and will compose the sandbox,
%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
through test generator tools, that identifies sensitive Android API, called during their execution. 
%\kn{This sentence seems to miss something "what" happens through test generation tools.}
These tools investigate program behavior through resource accesses realized by theses APIs. The second stage ensures that resources not accessed, or accessed differently than first stage, are not accessible by the apps. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

@@

Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet. Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}. Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the android operating system. Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity. A significant issue with taint analysis is the cost of the tool itself hampering the performance. FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.

>>>>

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data~\cite{DBLP:journals/peerj-cs/MaassSCS16}. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application~\cite{DBLP:conf/esorics/BordoniCS17}. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software. Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, 
working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.

Google Play Store is the primary market source for Android apps, and has a flexible policy regarding the process of publishing apps. Therefore, every month many Android apps are cleared from it because of issues related to spyware and other types of malware \cite{DBLP:conf/msr/WangLL0X18}. For security reasons, Google Play list each app with the requested permission. However, many malicious apps usually request more permissions than their APIs normally would require~\cite{DBLP:conf/ccs/FeltCHSW11}. Those permissions are presented to the user during the installation of a new app, since Android version 6, but most of the users are careless since they just want the end product.~\cite{DBLP:conf/soups/FeltHEHCW12} 
%\kn{Is there some citation or blog entry atleast that has shown this to be the real case with users?}

Nowadays, malware becomes more stealthy and hackers learn how to avoid anti-virus signature checks, by obfuscating the native code~\cite{DBLP:journals/corr/abs-2002-04540}
%\kn{Here we should cite the work of String hound (https://dl.acm.org/doi/10.1145/3320269.3384745)}
, calling Java libraries, or even by creating root exploits, since the native code is allowed to directly make syscalls. Another approach to rooting is making a side attack aimed at a benign app to make a syscall, exploiting its native code to get root access. Those are kind of attack that usually tackled with the Android Mining Sandbox \cite{DBLP:conf/icse/JamrozikSZ16}.

@@

\textbf{The Android Mining Sandbox} concept is a sandboxing technique that consists of mining rules from an Android app, and use these rules to ensure system security. The sandboxing technique comprises of two steps. First, rules are mined and will compose the sandbox,
%\kn{I thought sandbox was an environment, now it is comprised of rules?}%
through test generator tools, that identifies sensitive Android API, called during their execution. 
%\kn{This sentence seems to miss something "what" happens through test generation tools.}
These tools investigate program behavior through resource accesses realized by theses APIs. The second stage ensures that resources not accessed, or accessed differently than first stage, are not accessible by the apps. So, if a malicious app requires access to resources, different from what was previously mined, the sandbox will prohibit this access.

@@

Android applications contain within themselves the risk that sensitive data, such as credit card details, device information can be leaked into public sinks like the internet. Taint analysis is a special type of static analysis that enables tracking of sensitive data within programs~\cite{boddenesec}. Wei et al.~\cite{weiissta} propose a scalable taint analysis for Android applications that applies traditional taint analysis techniques with targeted optimizations specific to the Android operating system. Flowdroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} improves on precision of traditional approaches by including context and flow sensitivity. A significant issue with taint analysis is the cost of the tool itself hampering the performance. FastDroid~\cite{ZHANG2021102161} mitigates this issue by introducing an intermediate light-weight abstraction to perform the analysis.

### 2021-06-03 introduction.tex
first update - little grammar corrections

That is, the main idea of mining sandboxes is to explore the set of calls to sensitive API methods of an app, using different approaches
for automatically testing Android applications. The analysis explores the apps behavior and records all calls to sensitive APIs.
A sandbox builds upon these calls during the exploratory phase. The sandbox could then block future calls to
other sensitive resources which diverge from those found in the exploratory phase. Therefore, the sandbox accuracy depends on the exploratory capabilities of each testing tool
used to mine the sandbox.

@@

We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
and here we discuss the results of a broader investigation
that also uses DroidXP to explains the performance of static and dynamic analysis
approaches for mining sandboxes. Altogether, this paper brings the following contributions:

\begin{itemize}
\item A replication of the \blls study that better clarifies the performance of
  dynamic analysis tools for mining Android sandboxes.

>>>>

@@

We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
and here we discuss the results of a broader investigation
that also uses DroidXP to explain the performance of static and dynamic analysis
approaches for mining sandboxes. Altogether, this paper brings the following contributions:

\begin{itemize}
\item A replication of the \blls that better clarifies the performance of
  dynamic analysis tools for mining Android sandboxes.

### 2021-06-03 setup.tex
first update - little grammar corrections

The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
sandboxes, based on the calls to sensitive APIs from 102 pairs (benign / malign) of Android apps. In their work, \emph{performance} is
measured as the total number of malwares a sandbox is able to identify when comparing the calls to sensitive APIs made by
the benign and malign versions of the app. A \emph{hit} occurs whenever a sandbox finds that the malicious version of an app calls
additional sensitive APIs, in comparison to the calls from the corresponding benign version.
Nonetheless, the \blls uses DroidFax to instrument the Android apps, even though DroidFax also
collects calls to sensitive APIs using static analysis algorithms. Since the \blls does not
computed the possible impact of DroidFax into the performance of the test generation tools,
here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results.

@@

After that, we replicated the analysis using a configuration of DroidXP that disables the DroidFax static analysis algorithm.
Using this new configuration, we executed the benchmark again, using the same dataset of Android apps, the same execution time,
and the same test case generation tools.
The results of this replication allow us to compute the effective performance
of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
DroidFax static analysis algorithms.
Figure \ref{fig:setup} shows all the phases of our experimental, that explore all sensitive
resources access by both apps (B/M), and the optional configuration DroidXP, that disables DroidFax static analysis.

>>>>

The \blls reports the results of an empirical study that compares the performance of test generation tools to mine Android
sandboxes, based on the calls to sensitive APIs from 102 pairs (benign / malign) of Android apps. In their work, \emph{performance} is
measured as the total number of malwares a sandbox is able to identify when comparing the calls to sensitive APIs made by
the benign and malign versions of the app. A \emph{hit} occurs whenever a sandbox finds that the malicious version of an app calls
additional sensitive APIs, in comparison to the calls from the corresponding benign version.
Nonetheless, the \blls uses DroidFax to instrument the Android apps, even though DroidFax also
collects calls to sensitive APIs using static analysis algorithms. Since the \blls does not
compute the possible impact of DroidFax into the performance of the test generation tools,
here we replicate their work to understand the impact of the DroidFax static analysis algorithms into the \blls results.

@@

After that, we replicated the analysis using a configuration of DroidXP that disables the DroidFax static analysis algorithm.
Using this new configuration, we executed the benchmark again, using the same dataset of Android apps, the same execution time,
and the same test case generation tools.
The results of this replication allow us to compute the effective performance
of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
DroidFax static analysis algorithms.
Figure \ref{fig:setup} shows all the phases of our experiments, that explore all sensitive
resources access by both apps (B/M), and the optional configuration DroidXP, that disables DroidFax static analysis.
